\documentclass[a4paper,12pt]{article}
\usepackage[T1]{fontenc}
\usepackage{imakeidx}
\begin{document}
\tableofcontents

\section{Introduction}
In this document,we spend some words on policies in IT \index{policies}, what is a policy, why we have them, and how many 

\clearpage

\section{What is a policy?}
A policy is a defined set of \emph{rules} every emploee in a \emph{company} has to follow
Without this essential component there is no chance to have some sort of guidance and understand what it allowed and what it isn't. Some people might try to play safe and go by common sense but they might be mistaken in some of their decisions or actions

Every employee has a \emph{handbook} showing them all

\section{why we have them?}

The reason why we have them is to have a regulated working environment and be able to deal with Minstery of Defence 


\section{Type of policies}
\subsection{Environmental policies}
This is a set of rules to follow to make sure the environment is respected. A company that wants to comply to these policies will have to have a saved set of records showing how much fuel are the trucks using and how much is the distance the trucks are covering. The problem is what the company is entitled to do might not always respect real scenario since what we can do is just see on google maps which one is the most convenient road for a truck to take but we cannot guarantee the truck really did that road.
\clearpage
\printindex

\section{examples}
\subsection{Sony Playstation Network Hacking}

Sony was attacked in the past and did warn that the names, addresses and other personal data of about 77 million people with accounts on its PlayStation Network (PSN) have been stolen.

Gamers have been locked out of the network for a week, but the company took one week to realize what was happening

Sony said it discovered that between 17 and 19 April an "illegal and unauthorised person" got access to people's names, addresses, email address, birthdates, usernames, passwords, logins, security questions and more.

All gamers have been asked to sign lots of paperwork for free after which they have been rewarded with 3 games for free

But Sony upgraded its systems , announced it would finally introduce two-step verification, three years after Microsoft did the same for Xbox Live. There have been no widespread \emph{security breaches} since, although console networks remain vulnerable to concerted DDOS attacks - as seen when both PSN and Xbox Live failed over Christmas 2014.


\end{document}
